Self-Supervised Learning of Generalized Policies in adversarial domains

### 2021-05-25 doc/paper/paper.tex
minor change
changes

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
  0: Num[cell-has-martian] [k=1]
	1: Num[cell-has-target_martian] [k=1]
	2: Dist[col-has-agent;adjacent_col;col-has-target_martian] [k=4]]
\end{Verbatim}

@@

\subsubsection{Example of Game}
\begin{Verbatim}[fontsize=\footnotesize]
  M..M # M..M # M..M # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... #
  T..M # T..M # T..M # M..M # T..M # ...M # ..M. # ..M. # ..M. # ...M # ...M # ...T # ..T. # ..T. # .... #
  .... # .... # .... # T..M # ...M # ...T # ..T. # ..T. # ..T. # ...T # ...T # .... # .... # .... # .... #
  .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... #
  ..A. # .A.. # A... # A... # A... # A... # A... # .A.. # ..A. # ..A. # ...A # ...A # ...A # ..A. # ..A. #
\end{Verbatim}

\subsection{Space Invaders - v1}
\subsubsection{Description}
In this domain the agent can move to the right or to the left. The agent and the opponents have one action per turn. To win the agent has to kill all the opponents, for this he must shoot each of them. The agent kills an opponent if he moves into the column of the adversary, and he can only kill one for each shoot. The adversary has three possible actions, left, right and down, all the adversaries move in the same direction. The agent cannot be destroyed by the opponents.

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
  0: Num[cell-has-martian] [k=1]
	1: Num[cell-has-target_martian] [k=1]
	2: Dist[col-has-agent;adjacent_col;col-has-target_martian] [k=4]]
\end{Verbatim}

\subsubsection{Policy}
\begin{Verbatim}[fontsize=\footnotesize]
  1. B>0 AND C>0 AND A=0 -> {A ·, B ↓, C ↑}
  2. B>0 AND C>0 -> {A ·, B ·, C ↓}
  3. B>0 AND C>0 AND A>0 -> {A ↓, B ·, C ↓}, {A ↓, B ·, C ↑}, {A ↓, B ·, C ·}, {A ·, B ·, C ↓}
  4. B>0 AND C=0 -> {A ·, B ·, C ↑}
  5. B>0 AND C=0 AND A=0 -> {A ·, B ·, C ↑}
\end{Verbatim}

\subsubsection{Example of Game}
\begin{Verbatim}[fontsize=\footnotesize]
  M..M # M..M # T..M # .... # .... # .... # .... # .... # .... # .... # .... #
  T..M # T..M # ...M # T..M # T..M # ...M # ..M. # ..M. # ..T. # .T.. # .... #
  .... # .... # .... # ...M # ...M # ...T # ..T. # ..T. # .... # .... # .... #
  .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... #
  ..A. # .A.. # A... # A... # .A.. # A... # A... # .A.. # ..A. # ..A. # .A.. #
\end{Verbatim}

@@

\subsection{Checkmate - v1}
\subsubsection{Description}
In this game the action space is equal to the number of cells in the grid. In order to win the agent has to do a checkmate in one movement. Otherwise he loses. In the version v0 white pieces have the king and the queen, and black pieces have the king.

>>>>

\subsubsection{Training instances:}
\begin{Verbatim}[fontsize=\footnotesize]
  #m...m#
  #m...M#
  #.....#
  #...A.#
\end{Verbatim}

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
(A) Num[cell-has-martian] [k=1]
(B) Bool[cell-has-target_martian] [k=1]
(C) Dist[col-has-agent;adjacent_col;col-has-target_martian] [k=4]
\end{Verbatim}

@@

\subsubsection{Example of Game}
\begin{Verbatim}[fontsize=\footnotesize]
  m..m # m..m # m..m # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... #
  M..m # M..m # M..m # m..m # M..m # ...m # ..m. # ..m. # ..m. # ...m # ...m # ...M # ..M. # ..M. # .... #
  .... # .... # .... # M..m # ...m # ...M # ..M. # ..M. # ..M. # ...M # ...M # .... # .... # .... # .... #
  .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... #
  ..A. # .A.. # A... # A... # A... # A... # A... # .A.. # ..A. # ..A. # ...A # ...A # ...A # ..A. # ..A. #
\end{Verbatim}

\subsection{Space Invaders - v1}
\subsubsection{Description}
In this domain the agent can move to the right or to the left. TThe agent has two actions per turn and the adversary one. To win the agent has to kill all the opponents, for this he must shoot each of them. The agent kills an opponent if he moves into the column of the adversary, and he can only kill one for each shoot. The adversary has three possible actions, left, right and down, all the adversaries move in the same direction. The agent cannot be destroyed by the opponents.

\subsubsection{Training instances:}
\begin{Verbatim}[fontsize=\footnotesize]
  #m...m#
  #m...M#
  #.....#
  #...A.#
\end{Verbatim}

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
  (A) Num[cell-has-martian] [k=1]
  (B) Bool[cell-has-target_martian] [k=1]
  (C) Dist[col-has-agent;adjacent_col;col-has-target_martian] [k=4]
\end{Verbatim}

\subsubsection{Policy}
\begin{Verbatim}[fontsize=\footnotesize]
  1. B>0 AND C>0 AND A>0 -> {A ↓, B ·, C ↑},
                            {A ↓, B ·, C ↓},
                            {A ↓, B ·, C ·}
  2. B>0 AND C>0 AND A=0 -> {A ·, B ↓, C ↑}
  3. B>0 AND C=0 -> {A ·, B ·, C ↑}
  4. B>0 AND C>0 -> {A ·, B ·, C ↓}
  5. B>0 AND C=0 AND A=0 -> {A ·, B ·, C ↑}
\end{Verbatim}

\subsubsection{Example of Game}
\begin{Verbatim}[fontsize=\footnotesize]
  m..m # m..M # m..M # .... # .... # .... # .... # .... # .... # .... # .... # .... #
  m..M # m... # m... # m..M # m... # m... # .m.. # .M.. # .M.. # M... # M... # .... #
  .... # .... # .... # m... # M... # M... # .M.. # .... # .... # .... # .... # .... #
  .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... #
  ..A. # ...A # ..A. # ..A. # ...A # ..A. # ..A. # .A.. # ..A. # ..A. # .A.. # A... #
  1 (p)  1 (p)  2 (p)  1 (p)  1 (p)  2 (p)  1 (p)  1 (p)  2 (p)  1 (p)  1 (p)  2 (p)
\end{Verbatim}

@@

\subsection{Checkmate - v1}
\subsubsection{Description}
In this game the action space is equal to the number of cells in the grid. In order to win the agent has to do a checkmate in one movement. Otherwise he loses. In the version v0 white pieces have the king and the tower, and black pieces have the king.
